%
% abstract.tex
%
% Copyright (C) 2023 by Universidade Federal de Santa Catarina.
%
% Towards the Conception of GNSS Networks Based on Small Satellites
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 4.0
% International License. To view a copy of this license,
% visit http://creativecommons.org/licenses/by-sa/4.0/.
%

%
% \brief Abstract page.
%
% \author Gabriel Mariano Marcelino <gabriel.mm8@gmail.com>
%
% \version 1.1.0
%
% \date 2022/06/24
%

\chapter*{Abstract}

{\parindent0pt
%Redes de navegação e posicionamento utilizando constelações de satélites já são utilizadas a décadas tanto em escala global quanto regional. Mas até então, somente eram empregados satélites de grande porte operando em órbitas médias. Com o advento do satélites de pequeno porte como os CubeSats, novas estratégias de desenvolvimento e implementação vêm surgindo, visando principalmente simplificar e reduzir o custo de implantação de novos sistemas ou teste de novas tecnologias em órbita. Desta forma, este trabalho propõe um estudo da viabilidade do emprego de uma rede de posicionamento utilizando satélites de pequeno porte, visando principalmente redução de custo e simplificação da implantação deste tipo de sistema. Como forma de validar o conceito, propõe-se o desenvolvimento de uma carga útil que contendo um transmissor de sinais de GNSS, além da definição de uma missão completa para a validação do sistema e do conceito, através uma constelação.
Navigation and positioning networks using satellite constellations have been used for decades on both a global and regional scale. However, until now, only large satellites operating in medium orbits have been utilized. With the advent of small satellites such as CubeSats, new strategies for development and implementation are emerging, mainly aiming to simplify and reduce the cost of deploying new systems or testing new technologies in orbit. Thus, this work proposes a feasibility study on the use of a positioning network using small satellites, primarily aimed at cost reduction and the simplification of deploying this type of system. This study explores the use of recent technologies like chip-scale atomic clocks as time references for each satellite in the constellation and the implementation of the LoRa communication technique for the positioning signals emitted by the system. To validate the concept, the development of a payload containing a GNSS signal transmitter is proposed, along with defining a complete mission to validate the system and concept through a constellation.
}

\smallskip
\noindent \textbf{Keywords:} Embedded systems. Satellites. GNSS. Constellations.